Figures

### 2019-04-25 code/figures.rmd
Simplified figures.rmd code and re-added comment to helper file..

```{r transform_effect_and_compute_rma}
#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

#compute random effect meta-analysis of transformed effects
#'summarizer' is a sourced function
res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

>>>>

```{r transform_effect_and_compute_rma}
#Transform effect sizes to biserial correlations (pearson's correlations as is)
#then compute random effects meta-analyses per effect
#'transform_MA' and 'summarizer' are sourced functions
res <- dat %>% 
  split(.$effect) %>%  #necessary step otherwise the function is applied overall
  map(transform_MA) %>% #apply function each effect in the list
  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```
